### 2019-10-04 submission/manuscript.Rmd
Add figures

<!--- \includegraphics{figure_1.png} -->

**Figure 1. Caption caption caption.** Footnotes footnotes footnotes.

* Timeline of mothur/QIIME/etc citations
* Timeline of SRA deposits / 16S/microbiome in PubMed

**Figure 2. Caption caption caption.** Footnotes footnotes footnotes.

* Screenshot of mothur welcoming page

**Figure 3. Caption caption caption.** Footnotes footnotes footnotes.

* Screenshot of mothur homepage

>>>>

\includegraphics{figure_1.png}

**Figure 1. mothur has consistently been a popular software package over the past ten years with a total of more than 8,800 citations.** Citation data taken from the Web of Science (https://www.webofscience.com) on October 1, 2019. Data from 2019 are incomplete.

\includegraphics{figure_2.png}

**Figure 2. The mothur homepage.** From the mothur home page at www.mothur.org, users can download mothur, access a user forum, navigate a wiki with extensive documentation, join the mothur facebook group, and subscribe to the mothur mailing list.

\includegraphics{figure_3.png}

**Figure 3. The start up window when running mothur in Mac OS X in the interactive mode.** mothur can also be run on Windows or Linux. In the interactive mode users enter individual commands at the mothur prompt. Alternatively, users may run mothur by supplying commands from the command line or using batch scripts.

### 2019-10-04 submission/manuscript.tex
Add figures

\textbf{Figure 1. Caption caption caption.} Footnotes footnotes
footnotes.

\begin{itemize}
\tightlist
\item
  Timeline of mothur/QIIME/etc citations
\item
  Timeline of SRA deposits / 16S/microbiome in PubMed
\end{itemize}

\textbf{Figure 2. Caption caption caption.} Footnotes footnotes
footnotes.

\begin{itemize}
\tightlist
\item
  Screenshot of mothur welcoming page
\end{itemize}

\textbf{Figure 3. Caption caption caption.} Footnotes footnotes
footnotes.

\begin{itemize}
\tightlist
\item
  Screenshot of mothur homepage
\end{itemize}

>>>>

\includegraphics{figure_1.png}

\textbf{Figure 1. mothur has consistently been a popular software
package over the past ten years with a total of more than 8,800
citations.} Citation data taken from the Web of Science
(\url{https://www.webofscience.com}) on October 1, 2019. Data from 2019
are incomplete.

\includegraphics{figure_2.png}

\textbf{Figure 2. The mothur homepage.} From the mothur home page at
www.mothur.org, users can download mothur, access a user forum, navigate
a wiki with extensive documentation, join the mothur facebook group, and
subscribe to the mothur mailing list.

\includegraphics{figure_3.png}

\textbf{Figure 3. The start up window when running mothur in Mac OS X in
the interactive mode.} mothur can also be run on Windows or Linux. In
the interactive mode users enter individual commands at the mothur
prompt. Alternatively, users may run mothur by supplying commands from
the command line or using batch scripts.
